Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names

### 2019-11-15 paper/section_5_experiments.tex
Add baseline description

@@

Table~\ref{tab:results} shows the BLEU, ROUGE
,METEOR, and CIDEr metrics on GoodNews and NYTimes800k. We show two best
results from the previous state-of-the-art~\cite{Biten2019GoodNews}. Note that
the numbers reported here are slightly different from the original paper since
we had to remove a few samples from the test set where the image is no longer
available.~\cite{Biten2019GoodNews} also did some post-processing on the
ground-truth captions such as removing contractions and non-ASCII characters,
both of which we did not do. Despite these differences, the final metrics
are the same if rounded to the nearest whole number.

>>>>

\subsection{Baselines and Model Variants}

We show two previous state-of-the-art
models \textit{Biten (Avg + CtxIns)} and \textit{Biten (TBB +
	AttIns)}~\cite{Biten2019GoodNews}. To provide a fair comparison we used the
full caption results released by Biten \etal~\cite{Biten2019GoodNews} and
re-evaluated them using our evaluation pipeline and slightly different test set
(which we
have because of
broken image URLs). The final metrics are the same as originally reported if
rounded to the nearest
whole number.

We evaluate a few key modelling choices: the decoder type (\textit{LSTM} or
\textit{Transformer}), the text encoder type (\textit{GloVe} or
\textit{weighted RoBERTa}), the additional context domains
(\textit{location-aware} and \textit{face attention}), and word copying
(\textit{copying}). \verify{We keep the total number of trainable parameter for
each
model to within 7\% of one another other (148 million to 159 million), with the
unavoidable exceptions of
models employing \textit{location-aware} (*****), \textit{face attention} (171
million), and
\textit{copying} (207 million).}

@@

Table~\ref{tab:results} shows the BLEU, ROUGE, METEOR, and CIDEr metrics on
GoodNews and NYTimes800k.

\eat{The due primarily to broken image links the numbers in the table are
slightly different to what was previously reported~\cite{Biten2019GoodNews}.
Note that
the numbers reported here are slightly different from the original paper since
we had to remove a few samples from the test set where the image is no longer
available.~\cite{Biten2019GoodNews} also did some post-processing on the
ground-truth captions such as removing contractions and non-ASCII characters,
both of which we did not do. Despite these differences, the final metrics
are the same if rounded to the nearest whole number.}
